A Switching Planner for Combined Task and Observation Planning

### 2010-11-24 code/subarchitectures/planner.sa/trunk/src/latex/ICAPS-2011/dtpddl.tex
Not sure what this change is
Forgot this one last change

Because PPDDL cannot model domains that feature partial observability,
we developed an extension of that language, called DTPDDL. This can
express probabilistic models of the sensing consequences of acting, to
quantitatively capture unreliability in perception. That expressive
power is achieved by incorporating perceptual analogues of fluent,
predicate, and action definitions. In detail, we have declarations of
state characterising predicate and fluent symbols according to the
PPDDL syntax. In addition, we allow two other declarative blocks, for
perceptual predicates and fluents respectively. For example, suppose
our robot is tasked with exploring {\em locations} in order to
identify the whereabouts of a {\em visual-object}. We must describe
state and perceptual facts that model the {\em true}, resp. perceived,
locations of objects. In DTPDDL, these declarations appear as:

@@

\noindent In a slight departure from PPDDL, we suppose that
$\pp{look-for-object}$ has an effect on the state. That is, its
execution incurs a penalty, $3$, corresponding to the {\em cost} of
performing the visual search.\footnote{In PPDDL {\em reward} is a {\em
reserved word}, and occurs in {\em increased} and {\em decreased}
clauses of operator schemata. In that setting, {\em reward} is
interpreted as accumulated (resp. instantaneous) rewards and
penalties.}

@@

\noindent Here, the {\em execution} clause is a lifted description of
the sense action-precondition -- I.e,
$(\pp{look-for-object}~\pp{DORA}~\pp{box}~\pp{office}) =
\poss_\stochActions(\pp{vision}~\pp{DORA}~\pp{box}~\pp{office})$. Above,
we include a redundant state-precondition, $(=(\pp{is-in}~?r)?l)$ in
order to fully demonstrate the syntax. Interpreting the above schema,
if action $(\pp{look-for-object}~\pp{DORA}~\pp{box}~\pp{office})$ is
executed, there is a $0.8$ chance of perceiving the box if it is in
the $\pp{office}$, and otherwise a $0.1$ of perceiving it.

The syntax and semantics for describing initial state distributions in
DTPDDL is taken verbatim from PPDDL. It is useful to present that
factored tree-like structure here, in order to aid us when discussing
sequential planning in POMDP determinisations. The distribution is
expressed in a tree-like structure of terms. Each term is either: (1)
atomic, e.g., $(=(\pp{location}~\pp{box})~\pp{office})$, (2)
probabilistic, e.g., $(\pp{probabilistic}~p_1 (T_1) .. p_n (T_n))$
where $T_i$ are conjunctive, or (3) a conjunct over probabilistic and
atomic terms. The root term is always conjunctive, and the leaves are
atomic. For example, the starting distribution for $\pp{DORA}$ might
be described thusly:

>>>>

Because PPDDL cannot model domains that feature partial observability,
we developed an extension of that language, called DTPDDL. This can
express probabilistic models of the sensing consequences of acting, to
quantitatively capture unreliability in perception. That expressive
power is achieved by incorporating perceptual analogues of fluent,
predicate, and action definitions. In detail, we have declarations of
state characterising predicate and fluent symbols according to the
PPDDL syntax. In addition, we allow two other declarations, for
perceptual predicates and fluents respectively. For example, suppose
our robot is tasked with exploring {\em locations} in order to
identify the whereabouts of a {\em visual-object}. We must describe
state and perceptual facts that model the {\em true}, resp. perceived,
locations of objects. In DTPDDL, these declarations appear as:

@@

\noindent In a slight departure from PPDDL, we suppose that
$\pp{look-for-object}$ has an effect on the state. That is, its
execution incurs an instantaneous penalty, $3$, that corresponds to
the {\em cost} of performing the visual search.\footnote{In PPDDL {\em
reward} is a {\em reserved word}, and occurs in {\em increased} and
{\em decreased} terms in operator schemata. In that setting, {\em
reward} is interpreted as accumulated, whereas in DTPDDL it is
instantaneous.}

@@

\noindent Here, the {\em execution} declaration is a lifted description of
the sense action-precondition -- I.e,
$(\pp{look-for-object}~\pp{DORA}~\pp{box}~\pp{office}) =
\poss_\stochActions(\pp{vision}~\pp{DORA}~\pp{box}~\pp{office})$. Above,
we include a redundant state-precondition, $(=(\pp{is-in}~?r)?l)$ in
order to fully demonstrate the syntax. Interpreting the above schema,
if action $(\pp{look-for-object}~\pp{DORA}~\pp{box}~\pp{office})$ is
executed, there is a $0.8$ chance of perceiving the box if it is in
the $\pp{office}$, and otherwise a $0.1$ of perceiving it.

The syntax and semantics for describing initial state distributions in
DTPDDL is taken verbatim from PPDDL. It is useful to present that
factored tree-like structure here, in order to aid us when discussing
our switching continual planner. The distribution is expressed in a
tree-like structure of terms. Each term is either: (1) atomic, e.g., a
state proposition such as $(=(\pp{is-in}~\pp{box})~\pp{office})$,
(2) probabilistic, e.g., $(\pp{probabilistic}~p_1 (T_1) .. p_n (T_n))$
where $T_i$ are conjunctive, or (3) a conjunct over probabilistic and
atomic terms. The root term is always conjunctive, and the leaves are
atomic. For example, the starting distribution for $\pp{DORA}$ might
be described thusly:\footnote{In PDDL, $(\pp{:init}~T_1..T_n)$
expresses the conjunctive root of the tree -- I.e., the root node
$(\pp{and}~T_1..T_n)$. Also, we shall write $\prop$, rather than
$(\pp{and}~\prop)$, it a conjunctive term contain a single atomic
subterm.}
